# Standardized Vocabulary  

```{r covab_preamble, include = FALSE}
library(readr)
library(knitr)
library(kableExtra)
`%>%` <- magrittr::`%>%`
```

While many of the columns (e.g., location, standardized_location) are variable in their output, the types that are used to describe them are drawn from a standardized vocabulary. Here are the data standards for option 2 - long, with explanation for each.  
- `date`: YYYY-MM-DD  
- `location_type`: Continent, Country, State, Province  
- `location_standardized_type`: fips_code, iso_a3   
- `data_type`: For temporally dynamic data types, use `*_new` and `*_total` to represent new values for the current day versus cummulative values. cases_new, cases_total, deaths, deaths_total, recovered_new, recovered_total, beds_total, beds_new...  
  
Note - pull from tables in covid19R_data

## Current Location Types

```{r loc_type, echo = FALSE}
read_csv("https://github.com/Covid19R/covid19R_data/raw/master/controlled_vocabularies/location_type.csv", col_type = "cc") %>% 
  kable(format = "html") 
```

## Current Location Standardized Types

```{r loc_std_type, echo = FALSE}
read_csv("https://github.com/Covid19R/covid19R_data/raw/master/controlled_vocabularies/location_standardized_type.csv", col_type = "ccc") %>% 
  kable(format = "html") 
```

## Current Data Types
```{r dat_type, echo = FALSE}
read_csv("https://github.com/Covid19R/covid19R_data/raw/master/controlled_vocabularies/data_type.csv", col_type = "cc") %>% 
  kable(format = "html") 
```
