# Preparing and Submitting to CRAN

## A Checklist for pre-CRAN submission

Before submitting to CRAN, file an issue on your package with the following checklist. Fill it out as you go along with the preparation to submit steps outlined below.

```markdown
- [ ] Update the README.Rmd and re-knit

- [ ] Update the package site

- [ ] Update the package vignette, if you have one

- [ ] Update the package NEWS.md

- [ ] Make sure you pass build check

- [ ] Check your package with styler

- [ ] Check your package with goodpractice::gp()

- [ ] Run devtools checks and make sure you pass

- [ ] Update the package cran-comments.md

- [ ] Submit to CRAN with devtools::release()

```

## Guidance on executing your checklist.

Before submitting to CRAN, we'd ask that you

1. Make sure you pass build check (Check in the RMarkdown Build tab) with no errors, no warnings, no notes.

2. Update any vignettes with basic examples, the NEWS.md file with what is being released (or any changes from previous versions), and the README.Rmd with any final details.

3. Build a [pkgdown](https://pkgdown.r-lib.org/) website to help users. Make sure to link to it in your github repo.

```{r pkgdown, eval = FALSE}
# make a pkgdown website!
pkgdown::build_site()
```

4. Check your code to make sure it is is easy to read and well styled. This can be done easily with the [styler](https://styler.r-lib.org/) package.

```{r style, eval = FALSE}
styler::style_pkg()
```

5. Take a final check through to make sure your package is obeying best-practices using the [goodpractice](https://mangothecat.github.io/goodpractice/) library.

```{r best, eval = FALSE}
goodpractice::gp()
```

6. Execute final checks. First, make sure after making revisions from the above, you pass Build Check again. Then, walk through the following final checks provided by [devtools](https://devtools.r-lib.org/).

```{r, eval = FALSE}
# for release - checks!
devtools::check_win_release()
devtools::release_checks()
devtools::spell_check()
devtools::check_rhub()
```

7. Release! Again, using devtools (which will check you)!

```{r, eval = FALSE}
#-------------
# Release ####
#-------------
devtools::release()
```